Equalizer\\Programming and User Guide

### 2012-02-03 Developer/ProgrammingGuide/paper.tex

The images on the front page show the following applications build using
Equalizer: 
RTT DeltaGen\footnote{Image copyright Realtime Technology AG, 2008} [top
right], 
\textsf{Bino}, a stereo-capable, multi-display video player\footnote{\link{http://bino.nongnu.org/}}
[middle center],
a flow visualization application for climate research\footnote{Image
  courtesy of Computer Graphics and Multimedia Systems, University of
  Siegen} [middle right],
the \textsf{eqPly} polygonal renderer in a three-sided CAVE [bottom
left],
the \textsf{eVolve} volume renderer\footnote{Data set courtesy of
  General Electric, USA} [bottom center],
and the \textsf{eqNBody} gravitational n-body simulation, based on the
N-Body CUDA example [bottom right].

>>>>

The images on the front page show the following applications build using
Equalizer: RTT DeltaGen\footnote{Image copyright Realtime Technology AG, 2008}
[top right], \textsf{Bino}, a stereo-capable, multi-display video
player\footnote{\link{http://bino.nongnu.org/}} [middle center], a flow
visualization application for climate research\footnote{Image courtesy of
  Computer Graphics and Multimedia Systems, University of Siegen} [middle
  right], the \textsf{eqPly} polygonal renderer in a three-sided CAVE [bottom
  left], the \textsf{eVolve} volume renderer\footnote{Data set courtesy of
  General Electric, USA} [bottom center], and the
\textsf{RTNeuron}\footnote{\link{http://bluebrain.epfl.ch/}} application to
  visualize cortical circuit simulations [bottom right].
